### 2024-02-05 ms.qmd
Update ms.qmd

## Introduction
Behavioural flexibility, the ability to adjust the behaviour in response to internal or external changes in an adaptive way by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation [**REFS**]. Since behavioural flexibility can be affected by early environment [@jonson1976effect; @lui2017chronic], it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations, with a consequent impact on invasion success. Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.  
Here, we are particularly interested in the interactive contribution of prenatal temperature and Glucocorticoids (GCs). There are several reasons why we believe these two aspects are salient for studying behavioural flexibility in the context of invasion ecology. First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments. Furthermore, Gcs are one of the mechanisms mediating vertebrates’ response to changes in temperature that, at the same time, can have direct effects on animals' physiology and behaviour [@Crino_2023]. Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect]. In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].

>>>>

## Introduction
Behavioural flexibility, the ability to adjust the behaviour in response to internal or external changes in an adaptive way by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation [**REFS**]. 
**[Add a sentence here about how invassive species phenotype is advantageous when is plastic, but also mention that be plastic is not always fantastic if the environment constrain the development of adaptive phenotypes]**
Relative brain size, e.g., is a good predictor of behavioural plasticity and invasive success in mammals [@sol2008brain], birds [@sol2000behavioural; @sol2002behavioural], and reptiles and amphibians [@amiel_effects_2017]. Since the brain is especially snesitive during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success. Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.  
Here, we are particularly interested in the interactive contribution of prenatal temperature and Glucocorticoids (GCs). There are several reasons why we believe these two aspects are salient for studying behavioural flexibility in the context of invasion ecology. First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments. Furthermore, Gcs are one of the mechanisms mediating vertebrates’ response to changes in temperature that, at the same time, can have direct effects on animals' physiology and behaviour [@Crino_2023]. Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect]. In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
